Just Add IFC! A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-03-02 paper/retrofit.tex
More pushing through retrofit
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

Our overall plan will be to take a \textbf{{\color{red} target language}} with a formal
operational semantics and combine it with an \textit{{\color{blue} information
flow control language}}. While our technique will be indifferent to the
actual target language, for concreteness we give a simple, untyped lambda calculus to illustrate some examples, as well as express
how the language should be prepared for interoperability
in the style of Matthews and
Findler~\cite{Matthews:2007:OSM:1190216.1190220}.
We then equip this target language with primitives for implementing dynamic
information control in the style of LIO~\cite{lio}, which we will
describe in more detail shortly.

@@

In Figure~\ref{fig:ml}, we give a simple, untyped lambda calculus with
mutable references, prepared for combination with an
information flow control language.  The presentation is standard, but it
is worth paying some attention to the Felleisen-Hieb reduction
semantics~\cite{Felleisen:1992:RRS:136293.136297} used to define the
operational semantics of the system.  Our language defines an evaluation
context |tE|; however, the evaluation rules have been expressed in terms
of a different evaluation context |curlyRedE|,
following the approach of Matthews and
Findler~\cite{Matthews:2007:OSM:1190216.1190220} to combine operational
semantics of multiple languages.  To
derive the usual operational semantics for this language, the evaluation
context merely needs to be defined as |conf tS te @= tS, bracket tE te|.
However, when we combine this language with an IFC language, we must
reinterpret the meaning of this evaluation context.
In general, we require that a target language be expressed in terms
of some global machine state |tS|, some evaluation context |tE|,
some expressions |te|, some set of values |tv| and a \emph{deterministic}
reduction relation on full configurations $|tS| \times |tE| \times |te|$.

>>>>

Our overall plan will be to take a \textbf{{\color{red} target
language}} with a formal operational semantics and combine it with an
\textit{{\color{blue} information flow control language}}.  For example,
taking ECMAScript as the target language and combining it with our IFC
language should produce the formal semantics for SWAPI.  In this
presentation, we use a simple, untyped lambda calculus with mutable
references in place of ECMAScript, to demonstrate some of the key
properties without having too much detail; we discuss the proper
embedding in more detail in Section~\ref{sec:real}.

@@

In Figure~\ref{fig:ml}, we give a simple, untyped lambda calculus with
mutable references, prepared for combination with an
information flow control language.  The presentation is standard, and utilizes Felleisen-Hieb reduction
semantics~\cite{Felleisen:1992:RRS:136293.136297} to define the
operational semantics of the system.  Our language defines an evaluation
context |tE|; however, the evaluation rules have been expressed in terms
of a different evaluation context |curlyRedE|,
following the approach of Matthews and
Findler~\cite{Matthews:2007:OSM:1190216.1190220} to combine operational
semantics of multiple languages.  To
derive the usual operational semantics for this language, the evaluation
context merely needs to be defined as |conf tS te @= tS, bracket tE te|.
However, when we combine this language with an IFC language, we must
reinterpret the meaning of this evaluation context.
In general, we require that a target language be expressed in terms
of some global machine state |tS|, some evaluation context |tE|,
some expressions |te|, some set of values |tv| and a \emph{deterministic}
reduction relation on full configurations $|tS| \times |tE| \times |te|$.
